### 2015-05-10 evaluation.tex
update in evaluation
added experimental setup

\begin{figure}
\centering
\includegraphics[width=.99\linewidth]{experiments/figures/yieldmr_vs_yieldall.pdf}
\caption{draft}
\label{fig:plot1}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.99\linewidth]{experiments/figures/correlation.pdf}
\caption{draft}
\label{fig:plot2}
\end{figure}

@@

\noindent
\textbf{Experimental Setup}\xspace\xspace All experiments were performed on a ... machine running ..., LLVM 3.5; SMACK 1.5; Z3 4.3.2; Boogie rev. 4192 and \corral rev. 534.

>>>>

\begin{figure}
\centering
\includegraphics[width=.99\linewidth]{experiments/figures/yieldmr_vs_yieldall.pdf}
\caption{Scatter plot showing the runtime speedups that \corral achieves using \whoop with the \yieldmr instrumentation. The symbols $+$, $\circ$ and $\times$, represent a context-switch bound of 2, 5 and 9, respectively.}
\label{fig:plot}
\end{figure}

@@

\noindent
\textbf{Experimental Setup}\xspace\xspace We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5, Z3 4.3.2, Boogie rev. 4192 and \corral rev. 534.
